TBA

### 2019-10-11 paper.tex
Added result table

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{todonotes}

@@

\begin{equation*}
\label{eq:semitone-difference}
  \Delta f = 12\log_2\frac{f_0}{f_1}.
\end{equation*}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_discrimination.png}
  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }
  \label{fig:pitch-discrimination}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds.png}
  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }
  \label{fig:pitch-thresholds}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }
  \label{fig:pitch-thresholds-hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/target_errors.png}
  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
  \label{fig:target-errors}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{todonotes}

@@

\begin{equation}
\label{eq:semitone-difference}
  \Delta f = 12\log_2\frac{f_0}{f_1}.
\end{equation}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_discrimination.png}
  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds.png}
  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/target_errors.png}
  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
\end{figure}

\begin{table}
  \centering
  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
  \begin{tabular}{p{0.5cm}p{0.7cm}p{1cm}p{2cm}p{2.25cm}}
    \toprule
    &           & Setting      & Mean Angle Error [rad] & Spearman Correlation \\ \midrule
    \multirow{6}{*}{\textit{G1}}
    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.75, p < 0.001$ \\
    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.77, p < 0.001$ \\
    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.72, p < 0.001$ \\ \cline{3-5}
    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.36, p < 0.001$ \\
    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.49, p < 0.001$ \\
    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.48, p < 0.001$ \\ \midrule
    \multirow{6}{*}{\textit{G2}}
    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.10, p = 0.03$  \\
    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.13, p = 0.01$  \\
    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.21, p < 0.001$ \\\cline{3-5}
    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.03, p = 0.48$  \\
    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.31, p < 0.001$ \\
    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.40, p < 0.001$ \\ 
    \bottomrule
  \end{tabular}
\end{table}
